MSDS 7333 Case Study 06

### 2017-06-19 MSDS7333_CaseStudy06_MBaldree_BBrock_TElkins_AKelly.Rmd
udpates

```{r}
macs = unique(offlineSummary$mac)
macs
online = readData("online.final.trace.txt", subMacs = macs)
online$posXY = paste(online$posX, online$posY, sep = "-")
length(unique(online$posXY))
tabonlineXYA = table(online$posXY, online$angle)
#output shows measurements were taken at all angles throughout the floor
tabonlineXYA
```

Organize the data where each AP is in a column.

```{r}
onlineSummary = castOnline(online)
#confirm rejected AP is included
dim(onlineSummary)
names(onlineSummary)
```

<font color = "red">(Continued from baldree-case6.r)</font>

@@

@@

```{r}
#Iterate through 1 to 3 neighbors with 1 to 3 angles for each scenario to determine best combination
#for cross validation
for (ap in c("None", rejectedAP, chosenAP)){
  if (ap == "None"){
    test = onlineSummary
    train = offlineSummary
    newSignals = test[ , 6:12]
  } else {
    test = onlineSummary[, !(names(onlineSummary) %in% ap)]
    train = subset(offlineSummary, mac != ap)
    newSignals = test[,6:11]
  }

@@

Perform cross validation and plot for desired AP for a range of k's for each fold. We want to find k-NN estimates from 1...k and aggregate errors over the v folds.

@@

```{r}

# number of locations
permuteLocs = sample(unique(offlineSummary$posXY))

@@

```{r}
# matrix locations into folds
permuteLocs = matrix(permuteLocs, ncol = v, nrow = floor(length(permuteLocs)/v))
```
<font color = "Red"><b>&uarr; come back to this one &uarr;</b></font>

>>>>

First and foremost, let's display the unique MAC addresses: 
```{r}
macs = unique(offlineSummary$mac)
macs
```

```{r}
online = readData("online.final.trace.txt", subMacs = macs)
online$posXY = paste(online$posX, online$posY, sep = "-")
length(unique(online$posXY))
tabonlineXYA = table(online$posXY, online$angle)
#output shows measurements were taken at all angles throughout the floor
tabonlineXYA
```
This output shows the signal strengths at each angle. This will be useful later!
<font color = "red"><b>&uarr;Explain why &uarr;</b></font>

Organize the data where each AP is in a column. 
```{r}
onlineSummary = castOnline(online)
#confirm rejected AP is included
dim(onlineSummary)
names(onlineSummary)
```

@@

When it comes to the kNN, we will need to include the data which include the angles close to the point in question. As observed before, the angle matters! For this exercise, we will need to abide by the following outlines:

  * If one angle is desired, then we will include angles which match the rounded orientation of the new observation  
  * If we want two angles, two multiples of 45 degrees will be chosen in order to encapsulate the nw observation's orientation  
  * For three angles, the nearest 45 degree increment is chosen and either side will be used.

What if we didn't want to collapse the signal strengths across the *m* angles and, instead, we return a set of mx166 signals for each access point?

@@

Here, we begin by iterating through 1-3 neighbors at 1-3 angles for each combination to determine which will be best suited for cross-validation:

```{r}
for (ap in c("None", rejectedAP, chosenAP)){
  if (ap == "None"){
    test = onlineSummary
    train = offlineSummary
    newSignals = test[ , 6:12]
  } else {
    test = onlineSummary[, !(names(onlineSummary) %in% ap)]
    train = subset(offlineSummary, mac != ap)
    newSignals = test[,6:11]
  }

@@

Perform cross validation and plot for desired AP for a range of k's for each fold. We want to find k-NN estimates from 1 to k and aggregate errors over the v folds.

@@

```{r}
# number of locations
permuteLocs = sample(unique(offlineSummary$posXY))

@@

```{r}
# matrix locations into folds
permuteLocs = matrix(permuteLocs, ncol = v, nrow = floor(length(permuteLocs)/v))
```
<font color = "Red"><b>&uarr; come back to this one &uarr; For some reason it only runs after it throws an error (e.g.change matrix to sapply, run, change back and run again</b></font>
